---
title: "Model results"
output:
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/')
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(compare)
library(rjson)
library(data.table)

#setwd("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/")
# REMEMBER: the working directory of the R sessions and the working directory of the notebook are different things!!!!

```


```{r ce2}
dev<- read.table("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/data/gear/dev_data_new.tsv", sep="\t", header=FALSE, comment.char="#", na.strings=".", stringsAsFactors=FALSE, quote="", fill=TRUE)


#all_dev = merge(head(dev, -1), all, by.x=("V1"), by.y=("V5"))


#all_dev %>%
#  group_by(right.sembert)%>%
#  summarise(len_claim=mean(nchar(V3)), len_evidences = mean(nchar(V4)+nchar(V5)+nchar(V6)+nchar(V7)+nchar(V8)))

```


```{r ce4}
table_results <- function(results1, results2) {
  
  right1 = results1$right
  right2 = results2$right

  differing_rows = which(right1 != right2, arr.ind = FALSE)
  
  #bert_results <- cbind(bert_results, V5 = aggregation_results$V5) # I delete one row to match

  all = merge(results1, results2, by="V5", suffixes = c(".1",".2"))

  #all_dev = merge(dev, all, by=("V5"))
  all_dev = merge(dev, all, by.x=("V1"), by.y=("V5"))

  all_dev$ID <- seq.int(nrow(all_dev))


  all_dev$ID <- seq.int(nrow(all_dev))

  differing <- all_dev %>%
  filter(ID %in% differing_rows)
  


differing_improve <- all_dev %>%
  filter(ID %in% which(results1$right==0 & results2$right==1, arr.ind = FALSE))

differing_worse <- all_dev %>%
  filter(ID %in% which(results1$right==1 & results2$right==0, arr.ind = FALSE))

differing_improve %>%
  #filter(V1 %in% gold_dev$V4)%>%
  group_by(output.1, output.2)%>%
  summarise(counts = n(), proportion= n()/nrow(differing_improve), total_differing = nrow(differing_improve))%>%
  print()
  
differing_worse %>%
  #filter(V1 %in% gold_dev$V4)%>%
  group_by(output.1, output.2)%>%
  summarise(counts = n(), proportion= n()/nrow(differing_worse), total_differing = nrow(differing_worse))%>%
  print()

return(differing)
}

heatmap_errors <- function(results) {
  results$output = as.factor(results$output)
results$V4 = as.factor(results$V4)

results %>%
  group_by(output,V4) %>%
  summarise(count=n()) %>%
  as.data.frame()%>%
  ggplot(aes(x=output,y=V4,fill=count))+
  geom_tile()+ 
  geom_text(aes(label = round(count, 1))) +
  scale_fill_gradient(low = "white", high = "#4186BE") +
  labs(x="Predicted",y="Truth")+
  scale_x_discrete(labels = c("SUPPORTS", "REFUTES", "NEI"))+
  scale_y_discrete(labels = c("NEI","REFUTES", "SUPPORTS"), limits = rev)

}

```


## Results from base_bert

```{r ce5}
bert_results<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/bert_base/dev-results.tsv", header = FALSE, sep='\t')

bert_results <- bert_results %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(bert_results$right)/nrow(bert_results))

bert_results <- cbind(bert_results, V5 = dev$V1) # I delete one row to match

heatmap_errors(bert_results)

ggsave(file="visuals/confusion_matrix/base_bert.png", width=6, height=4, dpi=400)

```

## Results from sembert

```{r ce6}
sembert_12_results<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_all_tags/dev-results.tsv", header = FALSE, sep='\t')

sembert_12_results <- sembert_12_results %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(sembert_12_results$right)/nrow(sembert_12_results))

#table(sembert_12_results[, c("output", "V4")])

heatmap_errors(sembert_12_results)

ggsave(file="visuals/confusion_matrix/sembert_all_tags.png", width=6, height=4, dpi=400)


```

### Error comparison base_bert VS sembert

```{r ce7}

bert_small <- head(bert_results, -1)

d <- table_results(bert_small, sembert_12_results)


```


## Results from sembert with the DREAM mapping (sembert_dream)

```{r ce10}
dream_mapping <- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_dream/dev-results.tsv", header = FALSE, sep='\t')

dream_mapping_results <- dream_mapping %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(dream_mapping_results$right)/nrow(dream_mapping_results))

heatmap_errors(dream_mapping_results)

ggsave(file="visuals/confusion_matrix/sembert_dream.png", width=6, height=4, dpi=400)


```

### Comparison between base_bert and sembert_dream

```{r ce11}

d<-table_results(bert_results, dream_mapping_results)


```

## Results sembert with more tags (sembert_tags1)

```{r ce12}
tag_mapping<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_tags1/dev-results.tsv", header = FALSE, sep='\t')

tag_mapping_results <- tag_mapping %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(tag_mapping_results$right)/nrow(tag_mapping_results))

#mat <- table(tag_mapping_results[, c("output", "V4")])

heatmap_errors(tag_mapping_results)

ggsave(file="visuals/confusion_matrix/sembert_tags1.png", width=6, height=4, dpi=400)


```

### Comparison bert_base and sembert_tags1

```{r ce14}

differing<-table_results(bert_results, tag_mapping_results)


```

## Results sembert with OpenIE

```{r ce12}
oie<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_oie/dev-results.tsv", header = FALSE, sep='\t')

oie_results <- oie %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(oie_results$right)/nrow(oie_results))

heatmap_errors(oie_results)

ggsave(file="visuals/confusion_matrix/sembert_oie_tags1.png", width=6, height=4, dpi=400)


```



```{r ce12}
oie<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_oie_tags1/dev-results.tsv", header = FALSE, sep='\t')

oie_results <- oie %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(oie_results$right)/nrow(oie_results))

heatmap_errors(oie_results)

ggsave(file="visuals/confusion_matrix/sembert_oie_tags1.png", width=6, height=4, dpi=400)


```

### Comparison base_bert and oie

```{r ce14}

differing<-table_results(bert_results, oie_results)


```


## Results sembert with tags1+attention

```{r ce16}
att_tag<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_att_tags1/dev-results.tsv", header = FALSE, sep='\t')

att_tag_results <- att_tag %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(att_tag_results$right)/nrow(att_tag_results))

#mat <- table(tag_mapping_results[, c("output", "V4")])

heatmap_errors(att_tag_results)

ggsave(file="visuals/confusion_matrix/sembert_att_tags1.png", width=6, height=4, dpi=400)

```


## Results with gold evidence

### BERT

```{r ce6}
gold_b<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_bert_base/dev-results.tsv", header = FALSE, sep='\t')

gold_b_results <- gold_b %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  #filter(output!=2)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(gold_b_results$right)/nrow(gold_b_results))

#table(sembert_12_results[, c("output", "V4")])

heatmap_errors(gold_b_results)

ggsave(file="visuals/confusion_matrix/bert_gold.png", width=6, height=4, dpi=400)


```

### Sembert gold

```{r ce6}
gold<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_sembert_tags1/dev-results.tsv", header = FALSE, sep='\t')

gold_results <- gold %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  #filter(output!=2)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(gold_results$right)/nrow(gold_results))

#table(sembert_12_results[, c("output", "V4")])

heatmap_errors(gold_results)

ggsave(file="visuals/confusion_matrix/sembert_gold.png", width=6, height=4, dpi=400)

```


### Sembert gold little

```{r ce6}
gold<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_little/dev-results3.tsv", header = FALSE, sep='\t')

gold_results <- gold %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  #filter(output!=2)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(gold_results$right)/nrow(gold_results))

#table(sembert_12_results[, c("output", "V4")])

heatmap_errors(gold_results)

ggsave(file="visuals/confusion_matrix/sembert_gold_little.png", width=6, height=4, dpi=400)

```


```{r ce6}
gold<- read.csv("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_little/dev-results4.tsv", header = FALSE, sep='\t')

gold_results <- gold %>%
  #filter(V4!=2)%>%
  rowwise() %>%
  mutate(output= which.max(list(V1,V2,V3))-1)%>%
  #filter(output!=2)%>%
  mutate(right = sum(V4==output, na.rm=T))

print(sum(gold_results$right)/nrow(gold_results))

#table(sembert_12_results[, c("output", "V4")])

heatmap_errors(gold_results)

ggsave(file="visuals/confusion_matrix/sembert_gold_little.png", width=6, height=4, dpi=400)

```



```{r ce1, include=FALSE, eval=FALSE}
json_data <- fromJSON(paste(readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/data/gear/dev_srl_all.json"), collapse=""))

json_data[[1]]$evidence_srl$verbs[[1]]$tags

list_index = list()
list_i = list()

for (i in 1:length(json_data)){
  #print(i)
  list_index = append(list_index,json_data[[i]]$index)
  list_i = append(list_i, i)
} 

correspondence <- do.call(rbind.data.frame, Map('c', list_index, list_i))
colnames(correspondence) <- c("claim_index", "evidence_index")

```

```{r inspection1, include=FALSE, eval=FALSE}
#gold_unique <- gold_dev %>%
#  distinct(V3,.keep_all= TRUE)

#inspect = merge(differing, gold_dev, by.x=("V1"), by.y=("V4"), suffixes = c(".retrieved",".gold"))

go <- differing%>%
  filter(right.2==0)%>%
  filter(output.1==1)%>%
  filter(output.2==2)%>%
  select(V1, V3, V4,V5,V6, V7, V8)

```

```{r inspection2, include=FALSE, eval=FALSE}

instance <- go[1,]
instance

#index = 1852
#go %>%
#  filter(V5==index)%>%
#  print()

c <- correspondence%>%
  filter(claim_index == instance$V1) #index)

print(json_data[[strtoi(c[1,2])]]$claim_srl)

for (i in 1:nrow(c)){
  print(i)
  print(json_data[[strtoi(c[i,2])]]$evidence_srl)
}

```



```{r ce17, include=FALSE, eval=FALSE}
gold_dev<- read.table("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/data/gear/gold_evidence_dev.tsv", sep="\t", header=FALSE, comment.char="#", na.strings=".", stringsAsFactors=FALSE, quote="", fill=TRUE)
```


```{r ce18, include=FALSE, eval=FALSE}

library(jsonlite)
library(dplyr)

lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/data/retrieved/dev.ensembles.s10.jsonl")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
x <- bind_rows(lines)
```

```{r ce19, include=FALSE, eval=TRUE}
x <- scan("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/annotations/multi-hop-index.txt", what="", sep="\n")
# Separate elements by one or more whitepace
y <- strsplit(x, "[[:space:]]+")
```


### Multi-hop Error analysis

```{r ce20}
heatmap_errors_multi <- function(results) {
  results$output = as.factor(results$output)
results$V4 = as.factor(results$V4)

results %>%
  group_by(output,V4) %>%
  summarise(count=n()) %>%
  as.data.frame()%>%
  ggplot(aes(x=output,y=V4,fill=count))+
  geom_tile()+ 
  geom_text(aes(label = round(count, 1))) +
  scale_fill_gradient(low = "white", high = "#4186BE") +
  labs(x="Predicted",y="Truth")+
  scale_x_discrete(labels = c("SUPPORTS", "REFUTES", "NEI"))+
  scale_y_discrete(labels = c("REFUTES", "SUPPORTS"), limits = rev)

}

multi <- bert_results%>%
  filter(V5 %in% y)

print('bert_base')
print(sum(multi$right)/nrow(multi))

heatmap_errors_multi(multi)

ggsave(file="visuals/confusion_matrix/multi_hop_bert.png", width=6, height=3, dpi=400)


#multi_sem <- sembert_12_results%>%
#  filter(V5 %in% y)


#print(sum(multi_sem$right)/nrow(multi_sem))

#heatmap_errors_multi(multi_sem)

multi_sem_tags1 <- tag_mapping_results%>%
  filter(V5 %in% y)

print('sembert_tags1')
print(sum(multi_sem_tags1$right)/nrow(multi_sem_tags1))

heatmap_errors_multi(multi_sem_tags1)

ggsave(file="visuals/confusion_matrix/multi_hop_tags1.png", width=6, height=3, dpi=400)


# agg <- aggregation_results%>%
#   filter(V5 %in% y)
# 
# print(sum(agg$right)/nrow(agg))
# 
# heatmap_errors_multi(agg)
# 

print('sembert_dream')
dream <- dream_mapping_results%>%
   filter(V5 %in% y)
 
print(sum(dream$right)/nrow(dream))
 
heatmap_errors_multi(dream)
# 
#att <- att_tag_results%>%
#   filter(V5 %in% y)
# 
#print(sum(att$right)/nrow(att))
# 
#heatmap_errors_multi(att)
```








