---
title: "saliency"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/')
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(compare)
library(rjson)
library(data.table)
library(jsonlite)
library(tidyverse)
library(forcats)

#setwd("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/")
# REMEMBER: the working directory of the R sessions and the working directory of the notebook are different things!!!!

```

```{r load_data}
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/bert_base/saliency/F-base-bert-2_1_sal_l2")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric1 <- bind_rows(lines)
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/bert_base/saliency/F-base-bert-2_1_guided_l2")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric2 <- bind_rows(lines)
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/bert_base/saliency/F-base-bert-2_1_inputx_l2")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric3 <- bind_rows(lines)

list_metrics <- list(metric1,metric2,metric3)
list_metric_names <- c('saliency','guided','inputx')

#example1_1 <- metric1[3,] # SUPPORTS
#example1_2 <- metric2[3,] # SUPPORTS
#example1_3 <- metric3[3,] # SUPPORTS
```

```{r select_data}

normalized<-function(y) {

  x<-y[!is.na(y)]

  x<-(x - min(x)) / (max(x) - min(x))

  y[!is.na(y)]<-x

  return(y)
  }

get_format_sal <- function(list_metrics,id, list_metric_names, props=FALSE){
  final_list <- data.frame(V1=integer(), ID=factor(), stat=character(), order=factor()) 
  for(i in 1:length(list_metrics)) {
    example <- list_metrics[[i]][id,]

    token_names <- example%>%
      select(starts_with("tokens.token"))%>%
      t()%>%
      as.data.frame()


    token_values <- example%>%
      select(starts_with("tokens.0"))%>%
      t()%>%
      as.data.frame()


  token_values['ID'] <- token_names[,1]
  token_values$ID = as.factor(token_values$ID)
  token_values$V1 = as.numeric(token_values$V1)
  #token_values$V1 = apply(token_values[,1],2,normalized)

  token_values <- token_values%>%
    filter(ID != '[PAD]')
  
  if (props==TRUE){
    tag_names <- example%>%
      select(starts_with("props.prop"))%>%
      t()%>%
      as.data.frame()


    tag_values <- example%>%
      select(starts_with("props.0"))%>%
      t()%>%
      as.data.frame()
    
    tag_values['ID'] <- tag_names[,1]
    tag_values$ID = as.factor(tag_values$ID)
    tag_values$V1 = as.numeric(tag_values$V1)
    
    #print(colnames(tag_values))
    
    token_values <- rbind(token_values, tag_values)
    
  }
  
  token_values["stat"] <- as.factor(replicate(nrow(token_values), list_metric_names[i]))
  token_values['order'] <- c(1:nrow(token_values))
  token_values['order'] <- as.factor(token_values$order)

  final_list <- rbind(final_list, token_values)
  }
  


  return(final_list)
  
}
```

```{r plot_support}
metrics_list<- get_format_sal(list_metrics, 5, list_metric_names)

#token_values <- get_format_sal(example1_1)

metrics_list%>%
  #mutate(ID = fct_reorder(ID,order)) %>%
  #filter(ID!='NA')%>%
  ggplot(aes(x=order, y=stat, fill=V1)) + geom_tile()+
  scale_fill_gradient(low = "white", high = "#4186BE") +
  theme(axis.text.x = element_text(angle = 70, size = 7))+
  scale_x_discrete(labels=metrics_list[["ID"]][1:299])+
  #xlim(0, length(unique(metrics_list$ID)))
  labs(x="Token",y="Metric")
  

ggsave(file="visuals/saliency/bert_support_example.png", width=30, height=4, dpi=400)

```

```{r plot_refute}
metrics_list<- get_format_sal(list_metrics, 5, list_metric_names)

#token_values <- get_format_sal(example1_1)

metrics_list%>%
  #mutate(ID = fct_reorder(ID,order)) %>%
  #filter(ID!='NA')%>%
  ggplot(aes(x=order, y=stat, fill=V1)) + geom_tile()+
  scale_fill_gradient(low = "white", high = "#4186BE") +
  theme(axis.text.x = element_text(angle = 70, size = 7))+
  scale_x_discrete(labels=metrics_list[["ID"]][1:299])+
  #xlim(0, length(unique(metrics_list$ID)))
  labs(x="Token",y="Metric")
  

ggsave(file="visuals/saliency/bert_refute_example.png", width=30, height=4, dpi=400)

```

## Sembert


```{r load_data_s}
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_all_tags/saliency/scores_sal_l2_1")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric11 <- bind_rows(lines)
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_all_tags/saliency/scores_guided_l2_1")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric21 <- bind_rows(lines)
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/sembert_all_tags/saliency/scores_inputx_l2_1")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric31 <- bind_rows(lines)

list_metrics <- list(metric11,metric21,metric31)
list_metric_names <- c('saliency_l2','guided_l2','inputx_l2')

#example1_1 <- metric1[3,] # SUPPORTS
#example1_2 <- metric2[3,] # SUPPORTS
#example1_3 <- metric3[3,] # SUPPORTS
```


```{r plot_support_s}
for (i in 1:range(10)){
  print(i)
metrics_list<- get_format_sal(list_metrics, i, list_metric_names, props = TRUE)

#token_values <- get_format_sal(example1_1)

metrics_list%>%
  #mutate(ID = fct_reorder(ID,order)) %>%
  #filter(ID!='NA')%>%
  ggplot(aes(x=order, y=stat, fill=V1)) + geom_tile()+
  scale_fill_gradient(low = "white", high = "#4186BE") +
  theme(axis.text.x = element_text(angle = 70, size = 7))+
  scale_x_discrete(labels=metrics_list[["ID"]][1:299])+
  #xlim(0, length(unique(metrics_list$ID)))
  labs(x="Token",y="Metric")

name_file = paste0("visuals/saliency/sembert_example", as.character(i))
name_file =paste0(name_file, '.png')

ggsave(file=name_file, width=30, height=4, dpi=400)

}
  

#ggsave(file="image1_s.png", width=30, height=4, dpi=400)

```

## Sembert Gold


```{r load_data_s}

lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_sembert_tags1/saliency/scores_sal_l2_1")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric11 <- bind_rows(lines)
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_sembert_tags1/saliency/scores_guided_l2_1")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric21 <- bind_rows(lines)
lines <- readLines("C:/Users/bcalvo/Box/bcalvo/Claim-Verification-FakeNews/experiment-5/outputs/gold_sembert_tags1/saliency/scores_inputx_l2_1")
lines <- lapply(lines, fromJSON)
lines <- lapply(lines, unlist)
metric31 <- bind_rows(lines)

list_metrics <- list(metric11,metric21,metric31)
list_metric_names <- c('saliency_l2','guided_l2','inputx_l2')

# 10 is refutes example
# 1 is supports example
```


```{r plot_support_s}
#for (i in 1:range(10)){
#  print(i)
metrics_list<- get_format_sal(list_metrics, 8, list_metric_names, props = TRUE)



metrics_list%>%
  #mutate(ID = fct_reorder(ID,order)) %>%
  #filter(ID!='NA')%>%
  ggplot(aes(x=order, y=stat, fill=V1)) + geom_tile()+
  scale_fill_gradient(low = "white", high = "#4186BE") +
  theme(axis.text.x = element_text(angle = 70, size = 7))+
  scale_x_discrete(labels=metrics_list[["ID"]][1:299])+
  #xlim(0, length(unique(metrics_list$ID)))
  labs(x="Token",y="Metric")

#name_file = paste0("image_gold", as.character(i))
#name_file =paste0(name_file, '.png')

#ggsave(file=name_file, width=30, height=4, dpi=400)

#}
  

ggsave(file="visuals/saliency/gold_example.png", width=30, height=4, dpi=400)

```


```{r props}

metrics_list<- get_format_sal(list_metrics, 8, list_metric_names, props = TRUE)

#token_values <- get_format_sal(example1_1)

metrics_list%>%
  #mutate(ID = fct_reorder(ID,order)) %>%
  filter(str_detect(row.names(metrics_list), "props"))%>%
  ggplot(aes(x=order, y=stat, fill=V1)) + geom_tile()+
  scale_fill_gradient(low = "white", high = "#4186BE") +
  theme(axis.text.x = element_text(angle = 70, size = 7))+
  scale_x_discrete(labels=list(1,2,3,4,5,6,7,8,9,10,11,12))+
  #xlim(0, length(unique(metrics_list$ID)))
  labs(x="Token",y="Metric")

```


4.133838653564453       -1.1518515348434448     -2.8087878227233887     0       19988
-1.8166931867599487     3.7368228435516357      -2.07185697555542       1       19989
3.038501024246216       -0.5944563150405884     -2.2964770793914795     0       19990
3.8639352321624756      -0.8662200570106506     -2.826799154281616      0       19991
-1.6927106380462646     3.4238221645355225      -1.829237937927246      1       19992
2.090590476989746       0.36400893330574036     -2.449695348739624      1       19993
-1.766148328781128      3.250563383102417       -1.5731141567230225     1       19994
3.982449769973755       -0.8585338592529297     -2.9916036128997803     0       19995
-3.0836873054504395     -2.198235511779785      5.581490993499756       2       19996
-1.9053245782852173     3.5374648571014404      -1.730604887008667      1       19997

19988   SUPPORTS        Pearl (Steven Universe) projects a holographic body.    She is a `` Gem '' , a fictional alien being that exists as a magical gemstone projecting a holographic body .
19989   REFUTES American Sniper (book) is about cats and dogs only.     American Sniper : The Autobiography of the Most Lethal Sniper in U.S. Military History is an autobiography by United States Navy SEAL Chris Kyle , written with
 Scott McEwen and Jim DeFelice .
19990   SUPPORTS        Amy Winehouse died on 23 July 2011.     Amy Jade Winehouse -LRB- 14 September 1983 -- 23 July 2011 -RRB- was an English singer and songwriter .
19991   SUPPORTS        Java was formed by volcanic eruptions.  Formed mostly as the result of volcanic eruptions , Java is the 13th largest island in the world and the fifth largest in Indonesia .
19992   REFUTES Firefox is the second most popular dog breed.   , Firefox has between 9 % and 16 % of worldwide usage as a `` desktop '' browser , making it the second most popular web browser .
19993   REFUTES Hermit crabs are arachnids.     Hermit crabs are decapod crustaceans of the superfamily Paguroidea .    The Decapoda or decapods -LRB- literally `` ten-footed '' -RRB- are an order of crustaceans within the class Ma
lacostraca , including many familiar groups , such as crayfish , crabs , lobsters , prawns , and shrimp .
19994   REFUTES Michael Hutchence died on a boat.       On the morning of 22 November 1997 , Hutchence was found dead in his hotel room in Sydney .
19995   SUPPORTS        The Cyclades are located to the southeast of Greece's mainland. The Cyclades -LRB- -LSB- ˈsɪklədiːz -RSB- Κυκλάδες , -LSB- cikˈlaðes -RSB- -RRB- are an island group in the Aegean Sea , southeast of mainland
Greece and a former administrative prefecture of Greece .
19996   NOTENOUGHINFO   Theresa May worked the docks.   From 1977 until 1983 , she worked for the Bank of England , and from 1985 until 1997 at the Association for Payment Clearing Services , also serving as a councillor for Durnsf
ord in Merton . Theresa Mary May -LRB- née Brasier ; born 1 October 1956 -RRB- is a British politician who has served as Prime Minister of the United Kingdom since 2016 .      During her tenure she pursued reform of the Police Fede
ration , implemented a harder line on drugs policy including the banning of khat , oversaw the introduction of elected Police and Crime Commissioners , the deportation of Abu Qatada , the creation of the National Crime Agency and b
rought in additional restrictions on immigration .      She has been the Member of Parliament -LRB- MP -RRB- for Maidenhead since 1997 and Leader of the Conservative Party since July 2016 .   After unsuccessful attempts to be elect
ed to the House of Commons in 1992 and 1994 , she was elected as the MP for Maidenhead in the 1997 general election .
19997   REFUTES Trouble with the Curve is a television show.    Trouble with the Curve is a 2012 sports-drama film directed by Robert Lorenz , and starring Clint Eastwood , Amy Adams , Justin Timberlake , Matthew Lillard and John G
oodman .

